Portfolio conservation of metapopulations under\\climate change

### 2014-07-10 inst/ms/anderson-etal-metafolio.tex
Appendix B1 -> C1 (typo)
Remove response doc; input .bbl file for publication
Add missing sup fig references
Get main .tex file ready to submit

% SOM:
\newlabel{t:pars}{{B1}{2}}
\newlabel{f:stray}{{B1}{3}}
\newlabel{f:eg-sens}{{D1}{4}}
\newlabel{f:ret-corr}{{E1}{5}}
\newlabel{f:eg-sp-arma-full}{{F1}{6}}
\newlabel{f:eg-sp-arma-half}{{F2}{7}}
\newlabel{f:eg-sp-linear-full}{{F3}{8}}
\newlabel{f:eg-sp-linear-half}{{F4}{9}}
\newlabel{f:eg-n-arma-two}{{F5}{10}}
\newlabel{f:eg-n-arma-sixteen}{{F6}{11}}
\newlabel{f:eg-n-linear-two}{{F7}{12}}
\newlabel{f:eg-n-linear-sixteen}{{F8}{13}}

@@

\newcommand{\R}[1]{\label{#1}\linelabel{#1}}
\newcommand{\lr}[1]{line~\lineref{#1}}

@@

\begin{spacing}{1.1}
\setlength\parskip{0.11in}
\setlength\parindent{0in}
\include{response}
\setlength\parskip{0in}
\end{spacing}

@@

\bibliographystyle{ecology3}
\bibliography{jshort,ms}
%\input{anderson-etal-metafolio.bbl}

@@

 \setcounter{page}{1}
 \nolinenumbers
 \include{som}

>>>>

% SOM:
\newlabel{t:pars}{{B1}{2}}
\newlabel{f:stray}{{C1}{3}}
\newlabel{f:eg-sens}{{D1}{4}}
\newlabel{f:ret-corr}{{E1}{5}}
\newlabel{f:eg-sp-arma-full}{{F1}{6}}
\newlabel{f:eg-sp-arma-half}{{F2}{7}}
\newlabel{f:eg-sp-linear-full}{{F3}{8}}
\newlabel{f:eg-sp-linear-half}{{F4}{9}}
\newlabel{f:eg-n-arma-two}{{F5}{10}}
\newlabel{f:eg-n-arma-sixteen}{{F6}{11}}
\newlabel{f:eg-n-linear-two}{{F7}{12}}
\newlabel{f:eg-n-linear-sixteen}{{F8}{13}}
\newlabel{f:eg-n-squeeze-two}{{F9}{14}}
\newlabel{f:eg-n-squeeze-twelve}{{F10}{15}}

@@

%\newcommand{\R}[1]{\label{#1}\linelabel{#1}}
%\newcommand{\lr}[1]{line~\lineref{#1}}

@@

\begin{spacing}{1.1}
\setlength\parskip{0.11in}
\setlength\parindent{0in}
%\include{response}
\setlength\parskip{0in}
\end{spacing}

@@

%\bibliographystyle{ecology3}
%\bibliography{jshort,ms}
%\input{anderson-etal-metafolio.bbl}
\begin{thebibliography}{64}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{{\tt #1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi

\bibitem[{Allendorf et~al.(1997)Allendorf, Bayles, Bottom, Currens, Frissell,
  Hankin, Lichatowich, Nehlsen, Trotter, and Williams}]{allendorf1997}
Allendorf, F.~W., D.~Bayles, D.~L. Bottom, K.~P. Currens, C.~A. Frissell,
  D.~Hankin, J.~A. Lichatowich, W.~Nehlsen, P.~C. Trotter, and T.~H. Williams.
\newblock 1997.
\newblock Prioritizing {Pacific} salmon stocks for conservation.
\newblock Conserv. Biol. 11:140--152.

\bibitem[{Anderson(2014)}]{metafoliopkg}
Anderson, S.~C. 2014.
\newblock metafolio: Salmon metapopulation simulations for conservation
  planning through portfolio optimization. R package version 0.1.0.
  http://cran.r-project.org/package=metafolio.

\bibitem[{Anderson et~al.(2013)Anderson, Cooper, and Dulvy}]{anderson2013}
Anderson, S.~C., A.~B. Cooper, and N.~K. Dulvy.
\newblock 2013.
\newblock Ecological prophets: Quantifying metapopulation portfolio effects.
\newblock Methods Ecol. Evol. 4:971--981.

\bibitem[{Ando and Mallory(2012)}]{ando2012}
Ando, A.~W., and M.~L. Mallory.
\newblock 2012.
\newblock Optimal portfolio design to reduce climate-related conservation
  uncertainty in the {Prairie Pothole Region}.
\newblock Proc. Natl. Acad. Sci. U.S.A. 109:6484--6489.

\bibitem[{Balvanera et~al.(2006)Balvanera, Pfisterer, Buchmann, He,
  Nakashizuka, Raffaelli, and Schmid}]{balvanera2006}
Balvanera, P., A.~B. Pfisterer, N.~Buchmann, J.-S. He, T.~Nakashizuka,
  D.~Raffaelli, and B.~Schmid.
\newblock 2006.
\newblock Quantifying the evidence for biodiversity effects on ecosystem
  functioning and services.
\newblock Ecol. Lett. 9:1146--1156.

\bibitem[{Battin et~al.(2007)Battin, Wiley, Ruckelshaus, Palmer, Korb, Bartz,
  and Imaki}]{battin2007}
Battin, J., M.~W. Wiley, M.~H. Ruckelshaus, R.~N. Palmer, E.~Korb, K.~K. Bartz,
  and H.~Imaki.
\newblock 2007.
\newblock Projected impacts of climate change on salmon habitat restoration.
\newblock Proc. Natl. Acad. Sci. U.S.A. 104:6720--6725.

\bibitem[{Beechie et~al.(2013)Beechie, Imaki, Greene, Wade, Wu, Pess, Roni,
  Kimball, Stanford, Kiffney, and Mantua}]{beechie2013}
Beechie, T., H.~Imaki, J.~Greene, A.~Wade, H.~Wu, G.~Pess, P.~Roni, J.~Kimball,
  J.~Stanford, P.~Kiffney, and N.~Mantua.
\newblock 2013.
\newblock Restoring salmon habitat for a changing climate.
\newblock River Res. Applic. 29:939--960.

\bibitem[{Carlson and Satterthwaite(2011)}]{carlson2011}
Carlson, S.~M., and W.~H. Satterthwaite.
\newblock 2011.
\newblock Weakened portfolio effect in a collapsed salmon population complex.
\newblock Can. J. Fish. Aquat. Sci. 68:1579--1589.

\bibitem[{Cooper and Mangel(1999)}]{cooper1999}
Cooper, A.~B., and M.~Mangel.
\newblock 1999.
\newblock The dangers of ignoring metapopulation structure for the conservation
  of salmonids.
\newblock Fish. Bull. 97:213--226.

\bibitem[{Crozier et~al.(2008)Crozier, Hendry, Lawson, Quinn, Mantua, Battin,
  Shaw, and Huey}]{crozier2008}
Crozier, L.~G., A.~P. Hendry, P.~W. Lawson, T.~Quinn, N.~J. Mantua, J.~Battin,
  R.~G. Shaw, and R.~B. Huey.
\newblock 2008.
\newblock Potential responses to climate change in organisms with complex life
  histories: evolution and plasticity in {Pacific} salmon.
\newblock Evol. Appl. 1:252--270.

\bibitem[{de~Mazancourt et~al.(2013)de~Mazancourt, Isbell, Larocque, Berendse,
  De~Luca, Grace, Haegeman, Wayne~Polley, Roscher, Schmid, Tilman, van Ruijven,
  Weigelt, Wilsey, and Loreau}]{demazancourt2013}
de~Mazancourt, C., F.~Isbell, A.~Larocque, F.~Berendse, E.~De~Luca, J.~B.
  Grace, B.~Haegeman, H.~Wayne~Polley, C.~Roscher, B.~Schmid, D.~Tilman, J.~van
  Ruijven, A.~Weigelt, B.~J. Wilsey, and M.~Loreau.
\newblock 2013.
\newblock Predicting ecosystem stability from community composition and
  biodiversity.
\newblock Ecol. Lett. 16:617--625.

\bibitem[{DFO(2005)}]{dfo2005wsp}
DFO. 2005.
\newblock Canada's policy for conservation of wild {Pacific} salmon.
\newblock Technical report, Fisheries and Oceans Canada, Vancouver, BC.

\bibitem[{Dorner et~al.(2008)Dorner, Peterman, and Haeseker}]{dorner2008}
Dorner, B., R.~M. Peterman, and S.~L. Haeseker.
\newblock 2008.
\newblock Historical trends in productivity of 120 {Pacific} pink, chum, and
  sockeye salmon stocks reconstructed by using a {Kalman} filter.
\newblock Can. J. Fish. Aquat. Sci. 65:1842--1866.

\bibitem[{Eliason et~al.(2011)Eliason, Clark, Hague, Hanson, Gallagher,
  Jeffries, Gale, Patterson, Hinch, and Farrell}]{eliason2011}
Eliason, E.~J., T.~D. Clark, M.~J. Hague, L.~M. Hanson, Z.~S. Gallagher, K.~M.
  Jeffries, M.~K. Gale, D.~A. Patterson, S.~G. Hinch, and A.~P. Farrell.
\newblock 2011.
\newblock Differences in thermal tolerance among sockeye salmon populations.
\newblock Science 332:109--112.

\bibitem[{Elmqvist et~al.(2003)Elmqvist, Folke, Nystr{\"o}m, Peterson,
  Bengtsson, Walker, and Norberg}]{elmqvist2003}
Elmqvist, T., C.~Folke, M.~Nystr{\"o}m, G.~Peterson, J.~Bengtsson, B.~Walker,
  and J.~Norberg.
\newblock 2003.
\newblock Response diversity, ecosystem change, and resilience.
\newblock Front. Ecol. Environ. 1:488--494.

\bibitem[{Figge(2004)}]{figge2004}
Figge, F.
\newblock 2004.
\newblock Bio-folio: applying portfolio theory to biodiversity.
\newblock Biodivers. Conserv. 13:827--849.

\bibitem[{Fraser et~al.(2011)Fraser, Weir, Bernatchez, Hansen, and
  Taylor}]{fraser2011}
Fraser, D.~J., L.~K. Weir, L.~Bernatchez, M.~M. Hansen, and E.~B. Taylor.
\newblock 2011.
\newblock Extent and scale of local adaptation in salmonid fishes: review and
  meta-analysis.
\newblock Heredity 106:404--420.

\bibitem[{Gustafson et~al.(2007)Gustafson, Waples, Myers, Weitkamp, Bryant,
  Johnson, and Hard}]{gustafson2007}
Gustafson, R.~G., R.~S. Waples, J.~M. Myers, L.~A. Weitkamp, G.~J. Bryant,
  O.~W. Johnson, and J.~J. Hard.
\newblock 2007.
\newblock Pacific salmon extinctions: quantifying lost and remaining diversity.
\newblock Conserv. Biol. 21:1009--1020.

\bibitem[{Haak and Williams(2012)}]{haak2012}
Haak, A.~L., and J.~E. Williams.
\newblock 2012.
\newblock Spreading the risk: native trout management in a warmer and
  less-certain future.
\newblock N. Am. J. Fish. Manage. 32:387--401.

\bibitem[{Hannah et~al.(2002)Hannah, Midgley, Lovejoy, Bond, Bush, Lovett,
  Scott, and Woodward}]{hannah2002a}
Hannah, L., G.~F. Midgley, T.~Lovejoy, W.~J. Bond, M.~Bush, J.~C. Lovett,
  D.~Scott, and F.~I. Woodward.
\newblock 2002.
\newblock Conservation of biodiversity in a changing climate.
\newblock Conserv. Biol. 16:264--268.

\bibitem[{Hilborn et~al.(2003)Hilborn, Quinn, Schindler, and
  Rogers}]{hilborn2003}
Hilborn, R.~W., T.~Quinn, D.~Schindler, and D.~Rogers.
\newblock 2003.
\newblock Biocomplexity and fisheries sustainability.
\newblock Proc. Natl. Acad. Sci. U.S.A. 100:6564--6568.

\bibitem[{Hilborn and Walters(1992)}]{hilborn1992}
Hilborn, R.~W., and C.~Walters.
\newblock 1992.
\newblock Quantitative Fisheries Stock Assessment: Choice, Dynamics, and
  Uncertainty.
\newblock Chapman and Hall, London.

\bibitem[{Isaak and Rieman(2013)}]{isaak2013}
Isaak, D.~J., and B.~E. Rieman.
\newblock 2013.
\newblock Stream isotherm shifts from climate change and implications for
  distributions of ectothermic organisms.
\newblock Global Change Biol. 19:742--751.

\bibitem[{Isaak et~al.(2007)Isaak, Thurow, Rieman, and Dunham}]{isaak2007}
Isaak, D.~J., R.~F. Thurow, B.~E. Rieman, and J.~B. Dunham.
\newblock 2007.
\newblock Chinook salmon use of spawning patches: relative roles of habitat
  quality, size, and connectivity.
\newblock Ecol. Appl. 17:352--364.

\bibitem[{Isaak et~al.(2012)Isaak, Wollrab, Horan, and Chandler}]{isaak2012}
Isaak, D.~J., S.~Wollrab, D.~Horan, and G.~Chandler.
\newblock 2012.
\newblock Climate change effects on stream and river temperatures across the
  northwest U.S. from 1980--2009 and implications for salmonid fishes.
\newblock Climatic Change 113:499--524.

\bibitem[{Ives and Carpenter(2007)}]{ives2007}
Ives, A.~R., and S.~R. Carpenter.
\newblock 2007.
\newblock Stability and diversity of ecosystems.
\newblock Science 317:58--62.

\bibitem[{Jentsch et~al.(2007)Jentsch, Kreyling, and
  Beierkuhnlein}]{jentsch2007}
Jentsch, A., J.~Kreyling, and C.~Beierkuhnlein.
\newblock 2007.
\newblock A new generation of climate-change experiments: events, not trends.
\newblock Front. Ecol. Environ. 5:365--374.

\bibitem[{Johnson and Schindler(2013)}]{johnson2013a}
Johnson, S.~P., and D.~E. Schindler.
\newblock 2013.
\newblock Marine trophic diversity in an anadromous fish is linked to its
  life-history variation in fresh water.
\newblock Biol. Lett. 9:20120824.

\bibitem[{Koellner and Schmitz(2006)}]{koellner2006}
Koellner, T., and O.~J. Schmitz.
\newblock 2006.
\newblock Biodiversity, ecosystem function, and investment risk.
\newblock BioScience 56:977--985.

\bibitem[{Lackey(2003)}]{lackey2003}
Lackey, R.~T.
\newblock 2003.
\newblock {Pacific Northwest} salmon: forecasting their status in 2100.
\newblock Rev. Fish. Sci. 11:35--88.

\bibitem[{Lee and Jetz(2008)}]{lee2008}
Lee, T.~M., and W.~Jetz.
\newblock 2008.
\newblock Future battlegrounds for conservation under global change.
\newblock Proc. R. Soc. Lond. B 275:1261--1270.

\bibitem[{Luce et~al.(2013)Luce, Abatzoglou, and Holden}]{luce2013}
Luce, C.~H., J.~T. Abatzoglou, and Z.~A. Holden.
\newblock 2013.
\newblock The missing mountain water: slower westerlies decrease orographic
  enhancement in the {Pacific Northwest USA}.
\newblock Science 342:1360--1364.

\bibitem[{Luce and Holden(2009)}]{luce2009}
Luce, C.~H., and Z.~A. Holden.
\newblock 2009.
\newblock Declining annual streamflow distributions in the {Pacific Northwest
  United States}, 1948--2006.
\newblock Geophys. Res. Lett. 36.

\bibitem[{Mantua et~al.(2010)Mantua, Tohver, and Hamlet}]{mantua2010}
Mantua, N., I.~Tohver, and A.~Hamlet.
\newblock 2010.
\newblock Climate change impacts on streamflow extremes and summertime stream
  temperature and their possible consequences for freshwater salmon habitat in
  {Washington State}.
\newblock Climatic Change 102:187--223.

\bibitem[{Margules and Pressey(2000)}]{margules2000}
Margules, C.~R., and R.~L. Pressey.
\newblock 2000.
\newblock Systematic conservation planning.
\newblock Nature 405:243--253.

\bibitem[{Markowitz(1952)}]{markowitz1952}
Markowitz, H.
\newblock 1952.
\newblock Portfolio Selection.
\newblock J. Finance 7:77--91.

\bibitem[{McClure et~al.(2008{\natexlab{{\em a\/}}})McClure, Carlson, Beechie,
  Pess, Jorgensen, Sogard, Sultan, Holzer, Travis, Sanderson, Power, and
  Carmichael}]{mcclure2008a}
McClure, M.~M., S.~M. Carlson, T.~J. Beechie, G.~R. Pess, J.~C. Jorgensen,
  S.~M. Sogard, S.~E. Sultan, D.~M. Holzer, J.~Travis, B.~L. Sanderson, M.~E.
  Power, and R.~W. Carmichael.
\newblock 2008{\natexlab{{\em a\/}}}.
\newblock Evolutionary consequences of habitat loss for {Pacific} anadromous
  salmonids.
\newblock Evol. Appl. 1:300--318.

\bibitem[{McClure et~al.(2008{\natexlab{{\em b\/}}})McClure, Utter, Baldwin,
  Carmichael, Hassemer, Howell, Spruell, Cooney, Schaller, and
  Petrosky}]{mcclure2008b}
McClure, M.~M., F.~M. Utter, C.~Baldwin, R.~W. Carmichael, P.~F. Hassemer,
  P.~J. Howell, P.~Spruell, T.~D. Cooney, H.~A. Schaller, and C.~E. Petrosky.
\newblock 2008{\natexlab{{\em b\/}}}.
\newblock Evolutionary effects of alternative artificial propagation programs:
  implications for viability of endangered anadromous salmonids.
\newblock Evol. Appl. 1:356--375.

\bibitem[{McCullough(1999)}]{mccullough1999}
McCullough, D.~A., 1999.
\newblock A review and synthesis of effects of alterations to the water
  temperature regime on freshwater life stages of salmonids, with special
  reference to {Chinook} salmon.
\newblock EPA 910-R-99-010, US Environmental Protection Agency.

\bibitem[{McElhany et~al.(2000)McElhany, Ruckelshaus, Ford, Wainwright, and
  Bjorkstedt}]{mcelhany2000}
McElhany, P., M.~H. Ruckelshaus, M.~J. Ford, T.~C. Wainwright, and E.~P.
  Bjorkstedt, 2000.
\newblock {Viable Salmonid Populations} and the recovery of {Evolutionarily
  Significant Units}.
\newblock Technical Report NOAA Tech. Memo. NMFS-NWFSC-42, U.S. Deptartment of
  Commerce.

\bibitem[{Moore et~al.(2010)Moore, Mcclure, Rogers, and Schindler}]{moore2010}
Moore, J.~W., M.~Mcclure, L.~A. Rogers, and D.~E. Schindler.
\newblock 2010.
\newblock Synchronization and portfolio performance of threatened salmon.
\newblock Conserv. Lett. 3:340--348.

\bibitem[{Mori et~al.(2013)Mori, Furukawa, and Sasaki}]{mori2013}
Mori, A.~S., T.~Furukawa, and T.~Sasaki.
\newblock 2013.
\newblock Response diversity determines the resilience of ecosystems to
  environmental change.
\newblock Biol. Rev. 88:349--364.

\bibitem[{Patterson et~al.(2007)Patterson, Skibo, Barnes, Hills, and
  Macdonald}]{patterson2007}
Patterson, D.~A., K.~M. Skibo, D.~P. Barnes, J.~A. Hills, and J.~S. Macdonald.
\newblock 2007.
\newblock The influence of water temperature on time to surface for adult
  sockeye salmon carcasses and the limitations in estimating salmon carcasses
  in the {Fraser River, British Columbia}.
\newblock N. Am. J. Fish. Manage. 27:878--884.

\bibitem[{Pestes et~al.(2008)Pestes, Peterman, Bradford, and Wood}]{pestes2008}
Pestes, L.~R., R.~M. Peterman, M.~J. Bradford, and C.~C. Wood.
\newblock 2008.
\newblock Bayesian decision analysis for evaluating management options to
  promote recovery of a depleted salmon population.
\newblock Conserv. Biol. 22:351--361.

\bibitem[{Policansky and Magnuson(1998)}]{policansky1998}
Policansky, D., and J.~J. Magnuson.
\newblock 1998.
\newblock Genetics, metapopulations, and ecosystem management of fisheries.
\newblock Ecol. Appl. 8:S119--S123.

\bibitem[{Pressey et~al.(2007)Pressey, Cabeza, Watts, Cowling, and
  Wilson}]{pressey2007}
Pressey, R.~L., M.~Cabeza, M.~E. Watts, R.~M. Cowling, and K.~A. Wilson.
\newblock 2007.
\newblock Conservation planning in a changing world.
\newblock Trends Ecol. Evolut. 22:583--592.

\bibitem[{Quinn(2005)}]{quinn2005}
Quinn, T.~P.
\newblock 2005.
\newblock The Behaviour and Ecology of Pacific Salmon and Trout.
\newblock American Fisheries Society, Bethesda, Maryland.

\bibitem[{{\textsf{R} Core Team}(2013)}]{r2013}
{\textsf{R} Core Team}, 2013.
\newblock \textsf{R}: {A} language and environment for statistical computing.
\newblock \textsf{R} Foundation for Statistical Computing, Vienna, Austria.

\bibitem[{Rogers and Schindler(2008)}]{rogers2008}
Rogers, L.~A., and D.~E. Schindler.
\newblock 2008.
\newblock Asynchrony in population dynamics of sockeye salmon in southwest
  {Alaska}.
\newblock Oikos 117:1578--1586.

\bibitem[{Ruckelshaus et~al.(2002)Ruckelshaus, Levin, Johnson, and
  Kareiva}]{ruckelshaus2002}
Ruckelshaus, M.~H., P.~Levin, J.~B. Johnson, and P.~M. Kareiva.
\newblock 2002.
\newblock The {Pacific} salmon wars: what science brings to the challenge of
  recovering species.
\newblock Annu. Rev. Ecol. Syst. 33:665--706.

\bibitem[{Scheuerell et~al.(2006)Scheuerell, Hilborn, Ruckelshaus, Bartz,
  Lagueux, Haas, and Rawson}]{scheuerell2006}
Scheuerell, M.~D., R.~Hilborn, M.~H. Ruckelshaus, K.~K. Bartz, K.~M. Lagueux,
  A.~D. Haas, and K.~Rawson.
\newblock 2006.
\newblock The {Shiraz} model: a tool for incorporating anthropogenic effects
  and fish--habitat relationships in conservation planning.
\newblock Can. J. Fish. Aquat. Sci. 63:1596--1607.

\bibitem[{Schindler et~al.(2008)Schindler, Augerot, Fleishman, Mantua, Riddell,
  Ruckelshaus, Seeb, and Webster}]{schindler2008}
Schindler, D.~E., X.~Augerot, E.~Fleishman, N.~J. Mantua, B.~Riddell,
  M.~Ruckelshaus, J.~Seeb, and M.~Webster.
\newblock 2008.
\newblock Climate change, ecosystem impacts, and management for {Pacific}
  salmon.
\newblock Fisheries 33:502--506.

\bibitem[{Schindler et~al.(2010)Schindler, Hilborn, Chasco, Boatright, Quinn,
  Rogers, and Webster}]{schindler2010}
Schindler, D.~E., R.~Hilborn, B.~Chasco, C.~P. Boatright, T.~P. Quinn, L.~A.
  Rogers, and M.~S. Webster.
\newblock 2010.
\newblock Population diversity and the portfolio effect in an exploited
  species.
\newblock Nature 465:609--612.

\bibitem[{Schtickzelle and Quinn(2007)}]{schtickzelle2007}
Schtickzelle, N., and T.~P. Quinn.
\newblock 2007.
\newblock A metapopulation perspective for salmon and other anadromous fish.
\newblock Fish Fish. 8:297--314.

\bibitem[{Stockwell et~al.(2003)Stockwell, Hendry, and
  Kinnison}]{stockwell2003}
Stockwell, C., A.~Hendry, and M.~Kinnison.
\newblock 2003.
\newblock Contemporary evolution meets conservation biology.
\newblock Trends. Ecol. Evol. 18:94--101.

\bibitem[{Thibaut et~al.(2012)Thibaut, Connolly, and Sweatman}]{thibaut2012}
Thibaut, L., S.~R. Connolly, and H.~P.~A. Sweatman.
\newblock 2012.
\newblock Diversity and stability of herbivorous fishes on coral reefs.
\newblock Ecology 93:891--901.

\bibitem[{Thomas(2010)}]{thomas2010}
Thomas, C.~D.
\newblock 2010.
\newblock Climate, climate change and range boundaries.
\newblock Divers. Distrib. 16:488--495.

\bibitem[{Thomas et~al.(2004)Thomas, Cameron, Green, Bakkenes, Beaumont,
  Collingham, Erasmus, de~Siqueira, Grainger, Hannah, Hughes, Huntley, van
  Jaarsveld, Midgley, Miles, Ortega-Huerta, Townsend~Peterson, Phillips, and
  Williams}]{thomas2004}
Thomas, C.~D., A.~Cameron, R.~E. Green, M.~Bakkenes, L.~J. Beaumont, Y.~C.
  Collingham, B.~F.~N. Erasmus, M.~F. de~Siqueira, A.~Grainger, L.~Hannah,
  L.~Hughes, B.~Huntley, A.~S. van Jaarsveld, G.~F. Midgley, L.~Miles, M.~A.
  Ortega-Huerta, A.~Townsend~Peterson, O.~L. Phillips, and S.~E. Williams.
\newblock 2004.
\newblock Extinction risk from climate change.
\newblock Nature 427:145--148.

\bibitem[{Thorson et~al.(2014{\natexlab{{\em a\/}}})Thorson, Jensen, and
  Zipkin}]{thorson2014a}
Thorson, J.~T., O.~P. Jensen, and E.~F. Zipkin.
\newblock 2014{\natexlab{{\em a\/}}}.
\newblock How variable is recruitment for exploited marine fishes? A
  hierarchical model for testing life history theory.
\newblock Can. J. Fish. Aquat. Sci. 71:973--983.

\bibitem[{Thorson et~al.(2014{\natexlab{{\em b\/}}})Thorson, Scheuerell, Buhle,
  and Copeland}]{thorson2014}
Thorson, J.~T., M.~D. Scheuerell, E.~R. Buhle, and T.~Copeland.
\newblock 2014{\natexlab{{\em b\/}}}.
\newblock Spatial variation buffers temporal fluctuations in early juvenile
  survival for an endangered {Pacific} salmon.
\newblock J. Anim. Ecol. 83:157--167.

\bibitem[{Walther et~al.(2002)Walther, Post, Convey, Menzel, Parmesan, Beebee,
  Fromentin, Hoegh-Guldberg, and Bairlein}]{walther2002}
Walther, G.-R., E.~Post, P.~Convey, A.~Menzel, C.~Parmesan, T.~J.~C. Beebee,
  J.-M. Fromentin, O.~Hoegh-Guldberg, and F.~Bairlein.
\newblock 2002.
\newblock Ecological responses to recent climate change.
\newblock Nature 416:389--395.

\bibitem[{Waples et~al.(2009)Waples, Beechie, and Pess}]{waples2009}
Waples, R., T.~Beechie, and G.~R. Pess.
\newblock 2009.
\newblock Evolutionary history, habitat disturbance regimes, and anthropogenic
  changes: what do these mean for resilience of {Pacific} salmon populations?
\newblock Ecol. Soc. 14:3.

\bibitem[{Winfree and Kremen(2009)}]{winfree2009}
Winfree, R., and C.~Kremen.
\newblock 2009.
\newblock Are ecosystem services stabilized by differences among species? {A}
  test using crop pollination.
\newblock Proc. R. Soc. Lond. B 276:229--237.

\bibitem[{Yeakel et~al.(2014)Yeakel, Moore, Guimar{\~a}es, and
  de~Aguiar}]{yeakel2014}
Yeakel, J.~D., J.~W. Moore, P.~R. Guimar{\~a}es, and M.~A.~M. de~Aguiar.
\newblock 2014.
\newblock Synchronisation and stability in river metapopulation networks.
\newblock Ecol. Lett. 17:272--283.

\end{thebibliography}

@@

 %\setcounter{page}{1}
 %\nolinenumbers
 %\include{som}
